A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-01-30 sections/algorithm.tex
Simplifies worklist extension (same with proof)
Exvar and Hole notation

\paragraph{Existential Variables} ...

@@

\paragraph{Hole Notation}...

>>>>

\paragraph{Existential Variables} In order to find the unknown type $\tau$ in the declarative system,
\emph{existential variables} $\al, \bt$ are introduced to the algorithmic system.
They behave similarly to unification variables,
but their scoping is restricted by the position located in the worklist,
rather than globally defined
Any existential variable $\al$ should only be solved to
a well-formed type under the worklist before $\al$ is defined.
Thus the mono-type $\tau$ represented by the corresponding existential variable
is always well-formed under the corresponding declarative context.
In other words, the position of $\al$'s reflects the well-formedness restriction of $\tau$'s.

@@

\paragraph{Hole Notation}
We use the syntax $\Gm[\Gm_M]$ to denote the worklist $\Gm_L,\Gm_M,\Gm_R$,
where $\Gm$ is the worklist $\Gm_L,\bullet,\Gm_R$ with a hole ($\bullet$).
Hole notations with the same name implicitly shares the same structure $\Gm_L$ and $\Gm_R$.
A multi-hole notation splits the worklist into more parts.
For example, $\Gm[\al][\bt]$ means $\Gm_1,\al,\Gm_2,\bt,\Gm_3$.
